A holomorphic approach to branes in twisted~$M$-theory

### 2022-08-22 fivebranes/ops.tex
end of day

There is another way that observables are presented in a degenerate version of the BV formalism.
Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
We have seen that the observables~$\cO(\cE) = \Sym(\cE^\vee)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
That is, we consider the factorization algebra 
\[
U \subset M \mapsto \Sym \left(\cE_c(U) \right) 
\]
where $U \to \cE_c(U)$ is the cosheaf of compactly supported sections of the bundle~$E$.

@@

\parsec[s:localchar]

Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
The particular group of symmetries depends on the theory, so we will present some examples.

The holomorphic twist of the superconformal algebra in dimensions three and six is $\lie{osp}(6|2)$. 
So , in the case of the holomorphic twist of three and six-dimensional superconformal theories we consider the local character of operators with respect to the Lie algebra 
\beqn\label{eqn:cartan2}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
\eeqn
and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.

Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character. 
That is, the character of linear local operators.

\parsec[s:examples]

@@

\begin{eg}
Suppose that $V$ is the trivial bundle on $\C^n$ and consider the theory whose fields are
\[
\cE = \Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) 
\]
where the differential is just $\d_{dR} + \dbar$. 
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index which is immediate to compute:
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$, so counting local operators in this way is ill-defined. 
One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
\[
\frac{y}{(1-q_1)\cdots (1-q_n)} .
\]
The plethystic exponential of such an expression returns the local character
\[
\chi(q_1,\ldots,q_n,y) = \prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
\]
which now makes sense as a power series in the variables $y,q_1,\ldots,q_n$.
\end{eg}

@@

The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$ \cite{SWchar}. 
Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.

@@

\subsection{Operators on a single fivebrane}

We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables
\[
\Obs^{6d}_{\lie{u}(1)} 
\]
on $Z$.
We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs^{6d}_{\lie{u}(1)}(0)$ supported at~$0 \in \C^3$.

The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{\lie{u}(1)}$ with linear BRST differential is
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

Before moving on to characterizing local operators we take a brief moment to comment on the holographic appearance of the theory on a single fivebrane.

\parsec[s:fiverelatesingle]

In equation \eqref{eqn:limit2} we presented the universal factorization algebra of classical observables on the fivebrane 
\[
(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) 
\]
as a limit.
The first nonzero term in this limit diagram is 
\[
\clie_\bu(\cG_{1,c})
\]
where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$.

\begin{prop}
There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
\[
\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs^{6d}_{\lie{u}(1)} .
\]
\end{prop}

\begin{proof}
In weight $(-1)$ the abelian local Lie algebra takes the form
\[
\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
\]
where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
\beqn\label{eqn:weight-1a}
\begin{tikzcd}
\ul{odd} & \ul{even}\\
\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
\end{tikzcd}
\eeqn
On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
\[
\cO(\cE_{\lie{u}(1)}(U)) = \Sym(\Pi \overline{\cE}_{\lie{u}(1),c}^!(U)) .
\]
It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
The result then follows by applying ellipticity.
\end{proof}

We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.

\parsec[]

We know deduce the character of the holomorphic twist of the theory on a single fivebrane.
By the previous result we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.

\begin{lem}
\label{lem:single}
The $\Z \times \Z/2$ graded algebra of local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
V_0[[z_1,z_2,z_3]] \simeq \Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
\eeqn
\end{lem}

\begin{proof}
The jet expansion at $0 \in \C^3$ determines a map from the sections of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
On the formal disk all closed two-forms are automatically exact, which implies the lemma.
\end{proof}

\parsec

We move on to the straightforward computation of the character of local operators on a single fivebrane which we will present as the plethystic exponential of the character of linear local operators
\beqn
\chi^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = {\rm PExp} \big[f^{6d}_{\lie{u}(1)}(t_1,t_2,q,r) \big] .
\eeqn
According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{single}$.

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

Putting this all together we obtain the following.

\begin{prop}
\label{prop:6done}
The local character $\chi_{\lie{u}(1)}(q,t_1,t_2,r)$ of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
\beqn\label{eqn:6done}
f^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{prop}

Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}. 
For the case of the single fivebrane theory, this implies that the local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ form a representation for $E(3|6)$.

This fact also follows from our holographic analysis. 
In \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$. 
Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs_{\lie{u}(1)}^{6d}$.
On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
Combining these facts we see that $\Obs_{\lie{u}(1)}^{6d}(0)$ is a module for $E(3|6)$.

In \S \ref{s:kr} we will express this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.

\parsec

There are various degenerations, or specializations, of this character which are interesting to consider.
These specializations involve restricting the character above to a subalgebra of the full Cartan that we considered above.

One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
\beqn
f^{6d}_{\lie{u}(1)}(q,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
\eeqn
%They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
%In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
%\[
%\chi_{u(1)} (q,t_1=t_2=r=1) = \frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3} .
%\]

\parsec

Another specialization is related to a particular deformations by elements in the (twisted) superconformal algebra.
Recall that after performing the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry, the residual superconformal algebra is~$\lie{osp}(6|2)$. 
We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.

There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
The odd part of~$\lie{osp}(6|2)$ can be identified with 
\[
\C^3 \otimes \C^2 \oplus \Sym^2(\C^3) \otimes \C^2 
\]
where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations.

\begin{itemize}
\item The space $\C^3 \otimes \C^2$ is spanned by twisted supergravity fields of the form $\gamma = w_a \d z_i$. 
\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
\end{itemize}

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{\lie{u}(1)}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.

@@

\subsection{A conjectural description of a stack of two fivebranes}

In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
\[
\clie_{\bu}(\cG_{1,c}) \leftarrow \clie_{\bu}(\til \cG_{2,c}) \leftarrow \cdots .
\]
We now turn to the factorization algebra $\clie_{\bu}(\til \cG_{2,c})$.

Recall that $\til \cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\til \cG_{2} = \cG / \cG^{\geq 1}$. 
Since $\cG$ is concentrated in weights $\geq -1$ we see that $\til \cG_{2}$ is of the form
\[
\til \cG_2 = \cG_2 \ltimes \cG_1 
\]
where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
We focus mostly on the factorization algebra $\clie_\bu(\cG_{2,c})$.

We have already characterized the local dg Lie algebra $\cG_{2}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
We deduce that $\cG_2$ can be given a $\Z \times \Z/2$ grading where, as usual, we refer to $\Z$ as the cohomological grading and $\Z/2$ as the parity. 
With this lift to a $\Z \times \Z/2$ grading, the even part of $\cG_2$ is
\[
\Omega^{0,\bu}(Z, \T_Z) \oplus \Omega^{0,\bu}(Z) \otimes \lie{sl}(2) 
\]
with its natural cohomological grading by Dolbeault form type. 
The odd part of $\cG_2$ is
\[
\Omega^{1,\bu}(Z, K_Z^{-1/2}) \otimes \C^2 .
\]
The differential is $\dbar$ and the Lie bracket has been described in \S\ref{s:weight0}.

On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.

\parsec

We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$.

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

Combining these expressions we obtain the following.

\begin{prop} \label{prop:6dtwo}
The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
\beqn\label{eqn:6dtwo1}
\frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{prop}

Based on our discussion above we are led to the following conjecture.
\begin{conj}\label{conj:6dtwo}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\beqn\label{eqn:6dtwo}
f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{conj}

Following the general relationship between characters of holomorphic twists of supersymmetric theories and supersymmetric indices, this our conjecture for the supersymmetric index of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(2)$. 
Similarly, the index associated to the $\lie{gl}(2)$ theory is conjectured to be simply the product 
\[
\chi_{\lie{gl}(2)}^{6d} (q,t_1,t_2,r) = \chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) \cdot \chi_{\lie{u}(1)}^{6d}(q,t_1,t_2,r)
\]
where the index for the $\lie{u}(1)$ theory is given in the previous section. 
As a factorization algebra \brian{finish}

\parsec[]

The specialization of this index $t_1=t_2=r=1$ yields the single particle index
\[
\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
\]

\parsec[]

The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f^{6d}_{\lie{sl}(2)}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
\]
which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.

\subsection{Operators on a single membrane}

>>>>

There is another way that observables are presented in a degenerate version of the BV formalism.
Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
We have seen that the observables~$\cO(\cE) = \Sym(\cE^*)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
That is, we consider the factorization algebra 
\[
U \subset M \mapsto \Sym \left(\cE_c(U) \right) 
\]
where $U \to \cE_c(U)$ is the cosheaf of compactly supported sections of the bundle~$E$.

@@

\subsection{Local characters for topological-holomorphic theories}\label{s:localchar}

Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
We will restrict our attention to cases where $\cF$, as a graded vector space, is of the form $\Sym(\cE^*)$ or $\Sym(\cE_c)$ where $\cE$ is of the form \eqref{eqn:cE}.

The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries $H$, see \cite{SWchar}.
The particular group of symmetries depends on the theory, and we will present some examples momentarily.

By assumption, as a graded algebra, the algebra of local operators $\cF(0)$ of a topological-holomorphic theory is of the form
\beqn
\cF(0) = \Sym (\lie{s})
\eeqn
where $\lie{s}$ is a graded topological vector space which we interpret as the linear local operators.

We will also assume that the group of symmetries $H$ acting on $\cF(0)$ arises from an action of $H$ on the linear local operators $\lie{s}$. 
Denote by $f_{\cF}({\bf q})$ the character of $\lie{s}$ with respect to this group action---this is the so-called `single particle' character. 
The full character of $\cF(0)$ is then given as the plethystic exponential of this single particle character
\beqn
\chi_{\cF}({\bf q}) = {\rm PExp}\left[f_{\cF}({\bf q}) \right] .
\eeqn

\subsection{Examples}

@@

\begin{eg}
Suppose that $V$ is the trivial bundle on $\C^n$ and consider the theory whose fields are
\[
\cE = \Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) 
\]
where the differential is just $\d_{dR} + \dbar$. 
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) ,
\]
where $\lie{s} \simeq \frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]$ is (equivalent to) the space of linear local operators.

Consider the standard torus action $\C^\times \times \cdots \times \C^\times$ on $\C^n$. 
We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index (the character of the space of linear local operators) which is immediate to compute:
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$, so counting local operators in this way is ill-defined. 
One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
\[
\frac{y}{(1-q_1)\cdots (1-q_n)} .
\]
The plethystic exponential of such an expression returns the local character
\[
\chi(q_1,\ldots,q_n,y) = \prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
\]
which now makes sense as a power series in the variables $y,q_1,\ldots,q_n$.
\end{eg}

@@

The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.

@@

@@
